Constant-sized correlations are sufficient for robust self-testing of maximally entangled states with unbounded dimension

### 2019-05-02 Draft/draft.tex
Honghao: edits of section 3 and 4:

%=======================================
\section{The linear system game}
\label{sec:lsg}
%=======================================
In this section, we introduce a linear system game which is a component of the full test.
This game is designed to enforce relations that should be satisfied by 
Alice and Bob's observables. The inspiration comes from 
Slofstra's seminal work~\cite{slofstra2017}, in which he
embeds the group
\begin{align}
	K = \ip{ x,y,a,b:a^2=b^2=e, ab=ba, yay^{-1} = a, yby^{-1} = ab, xyx^{-1}=y^2}
\end{align}
into a linear system game such that the relations in the definition of $K$ can be derived from the
combination of the linear equations. Then he showed the difference between exact representations
and approximate representations of $K$, which implies that the set of quantum correlation is not closed.
\hf{We generalize the relation $xyx^{-1} = y^2$ and embed the 
following relation
$
uou^{-1} = o^r 
$
for some $r \in \N$ into a linear system game.}

%------------------------------------------------------------------------
\subsection{The embedding of $G$}
%------------------------------------------------------------------------
The main result of this subsection is summarized in the following theorem.
\begin{theorem}
	The relation $uou^{-1} = o^r$ can be embedded in a linear system game which has
	$n(r) := 18r+85$ variables and $m(r) := 17r + 77$ equations, where each equation has $3$ variables.
\end{theorem}
We prove this by constructing the solution group $\Gamma$ of the linear system game. 
We also prove some properties of the generators of $\Gamma$ along the way.

We embed $uou^{-1}= o^r$ into $\Gamma$ in three steps, which introduce two intermediate groups $G_0$ and $G_1$ defined below.
\begin{definition}	
\label{def:g0}
	The presentation of $G_0$ has order-$2$ generators:
	\begin{align*}
		\{o_i\}_{i=1}^{r} \cup \{u_i\}_{i=1}^5
	\end{align*}
	and relations:
	\begin{align*}
	&u_3 = u_2o_1u_2 && u_4 = u_2o_2u_2 \\
	&u_5 = u_1u_3u_1 && o_2 = u_1u_4u_1\\
	&u_5 = o_1 o_r o_1,
	\end{align*}
	and when $r$ is even
	\begin{align*}
	&o_{1+2j} = o_1o_{2j}o_1 && o_{2+2j} = o_2o_{1+2j}o_2&& \text{ for } j = 1 \dots r/2 - 1;
	\end{align*}
	when $r$ is odd
	\begin{align*}
	&o_3 = o_2o_1o_2 &&
	 o_{2+2j} =o_1o_{1+2j}o_1 && o_{3+2j} = o_2o_{2j+2}o_2 &&\text{ for } j = 1 \dots (r-3)/2.
	\end{align*}
\end{definition}
\begin{proposition}
	The group $G_0$ embeds the relation 
	\begin{align}
		(u_1u_2)^j o_1o_2 (u_2u_1)^j = (o_1o_2)^{r^j}, 
	\end{align}
	for any $ j \in \N$.
\end{proposition}
The proof follows the proof of Proposition~$4.8$ of Ref.~\cite{slofstra2017}
\begin{proof}
	We prove it by induction.
	Direct calculation gives us that
	\begin{align*} 
		u_1u_2 o_1o_2 u_2u_1 = &u_1 (u_2 o_1u_2) (u_2o_2 u_2) u_1 \\
	=& (u_1 u_3 u_1) (u_1 u_4 u_1)\\
	=& u_5 o_2\\
	=& o_1o_ro_1 o_2.
	\end{align*}
	Then we substitute the definitions of $o_k$ for $k = r \dots 3$ into the equation above and
	proves the $j=1$ case.

	Now assume the statement is true for $j = n$, then for $j = n+1$
	\begin{align*}
		(u_1u_2)^{n+1} o_1o_2 (u_2u_1)^{n+1} =& u_1u_2 (o_1o_2)^{r^n} u_2u_1 \\ 
		 =& (u_1u_2 o_1o_2 u_2u_1)^{r^n} \\
		 =& (o_1o_2)^{r^{n+1}},
	\end{align*}
	where from the first line to the second line, we insert $(u_2u_1)(u_1u_2)$ between every pair of $o_1o_2$.
	Hence, the statement is true.
\end{proof}
To better characterize all the conjugation relations above and simplify the form of $G_1$ defined below, 
we relabel $u_i$ and $o_i$'s
as $a_i$'s such that
\begin{align}
	a_j := 
	\begin{cases}
	 o_j \text{ for } j = 1,2 \\
	 u_{j-2} \text{ for } j = 3\dots 7 \\
	o_{j- 5} \text{ for } j = 8 \dots r+5.
	\end{cases}
\end{align}
Then we define the set $C(r)$ of tuples $(i,j,k)$ such that
\begin{align*}
	(i,j,k) \in C(r) \iff a_ia_ja_i = a_k.
\end{align*}
The size of $C(r)$ is $r+3$. 
%We can also employ some ordering of $C(r)$ such that $C(r,j)$ is a unique tuple for 
%$j = 1 \dots r+3$.
In this way, the group $G_0$ can be presented by
$
G_0  = \ip{ \{a_i\}_{i=1}^{r+5} : C(r) }.
$
Then we define the group $G_1$.
\begin{definition}
The presentation of $G_1$ has order-$2$ generators:
\begin{align*}
	\{a_i, b_i, c_i, d_i, v_i\}_{i=1}^{r+5}, f, g, \{h_{jk}\}_{(i,j,k) \in C(r)};
\end{align*}
and relations:
\begin{align*}
	&a_i = b_ic_i = fd_i = gv_i,&& fb_if =c_i &&\text{ for } i= 1 \dots r+5 \\
	&h_{jk}b_j c_k = e,&& d_ib_jd_i = c_k &&\text{ for all } (i,j,k) \in C(r).
\end{align*}
\end{definition}
Note that the group $G_1$ is slightly different from the group $K$ used in the proof of Lemma~$4.4$ of Ref.~\cite{slofstra2017}.
We introduce the generator $g$ so that later we can associate $f$ with $g$ in linear relations of the Magic Square game.
Such relations are important for the self-testing proof.
Two important properties of $G_1$ are given in propositions below.
The first property of $G_1$ was first proved in Lemma~$4.4$ of \cite{slofstra2017}.
\begin{proposition}
	The group $G_1$ embeds relation $x_ix_jx_i = x_k$ for all $(i,j,k) \in C(r)$.
\end{proposition}
\begin{proof}
	We first show that $d_i c_j d_i = b_k$, which is because
	\begin{align*}
		d_i c_j d_i = d_i (f b_j f) d_i = f (d_i b_j d_i) f = f c_k f = b_k.
	\end{align*}
	Then, we can prove that 
	\begin{align*}
		a_i a_j a_i = f d_i b_j c_j f d_i = (f d_i b_j d_i f)(f d_i c_j d_i f) = (f c_k f)(f b_k f) = b_k c_k = a_k. 
	\end{align*}
\end{proof}
\begin{proposition}
	In the group $G_1$, the generators $f$ and $g$ commute with $a_i$ for all $i = 1 \dots r+5$.
\end{proposition}
\begin{proof}
	We can check that
	\begin{align*}
		fa_i f a_i = d_i d_i = e && g a_i g a_i = v_i v_i  = e,
	\end{align*}
	for all $i = 1 \dots r+5$.
\end{proof}
Note that there are two types of conjugacy relations in $G_1$. One is of the form
$f b_i f = c_i$ for all $i = 1 \dots r+5$. The other one is of the form 
$d_ib_jd_i = c_k$ for all $(i,j,k) \in C(r)$. For each type of the conjugacy relations, 
we are going to embed it into a different set of linear relations in $\Gamma$.

\begin{definition}
\label{def:gamma}
The presentation of $\Gamma$ has order-$2$ generators:
\begin{align*}
	J, \{a_i, b_i, c_i, d_i, v_i,w_i,\{ k_{i,j} \}_{j=1}^5\}_{i=1}^{r+5}, \{f_i,g_i,m_i\}_{i=0}^2, \{h_{jk}\}_{(i,j,k) \in C(r)}, 
	\{\{ k_{l,j} \}_{j=1}^6\}_{l \in C(r)},
\end{align*}
and relations:
\begin{itemize}
\item for all $i = 1 \dots r+5$:
\begin{align*}
	&a_i = b_ic_i = f_0d_i = g_0v_i \\
	&g_2 a_i w_i = e \\
	&f_0 f_1 f_2 = e && b_i f_2 k_{i,1} = e && k_{i,1} k_{i,2} k_{i,3} = e\\
	&f_0 k_{i,3} k_{i,4} = e && c_i k_{i,4} k_{i,5} =e && f_1 k_{i,2} k_{i,5} = e,
\end{align*}
which embed $f_0 b_i f_0 = c_i$;
\item for all $ l = (i,j,k) \in C(r)$:
\begin{align*}
	&h_{jk}b_j c_k = e\\
	&d_i k_{l,1} f_2 = e && b_j f_2 k_{l,2} = e && k_{l,2} k_{l,3} k_{l,4} = e\\
	&d_i k_{l,4} k_{l,5} = e && c_k k_{l,5} k_{l,6} =e && k_{l,1} k_{l,3} k_{l,6} = e,
\end{align*}
which embed $d_i b_j d_i = c_k$;
\item relations of a Magic Square game:
\begin{align*}
	&f_0 f_1 f_2 = e && g_0 g_1 g_2 = e &&m_0 m_1 m_2 = e \\
	&f_0 g_2 m_0 = e && f_2 g_0 m_1 = e && f_1 g_1 m_2 = J,
\end{align*}
which embed $f_0 g_0 f_0 g_0 = J$ and $f_2 g_2 f_2 g_2 = J$;
\item $J$ commutes with all the other generators.
\end{itemize}
\end{definition}
The special properties of the generators of $\Gamma$ are summarized in the two propositions below.
\begin{proposition}
	The group $\Gamma$ embeds all the conjugacy relations of $G_1$.
	It also embeds the relations: $f_0 g_0 f_0 g_0 = J$ and $f_2 g_2 f_2 g_2 = J$.
\end{proposition}
The proof of the proposition above follows the proof of Proposition $4.2$ of Ref.~\cite{slofstra2017}.
\begin{proposition}
	In the group $\Gamma$, the generator $f_2$ commutes with $f_0$ and $a_i$ for all $i = 1 \dots r+5$;
	the generator $g_2$ commutes with $g_0$ and $a_i$ for all $i = 1 \dots r+5$.
\end{proposition}
\begin{proof}
	We show the commutativity property of $f_2$ as an example. The proof for $g_2$ is very similar.
	The commutativity between $f_0$ and $f_2$ is immediate from the relations.
	From the relation, we can also deduce that $f_2$ commutes with $b_i$ for all $i$.
	Since $a_i =b_ic_i = b_i f_0 b_i f_0$, we know $f_2$ commutes with $a_i$.
\end{proof}

%------------------------------------------------------------------------
\subsection{The representation of $\Gamma$}
%------------------------------------------------------------------------
In this section we give a representation of $\Gamma$ which is built upon the representation 
$\Psi_0$ of $G_0$ and $\Psi_1$ of $G_1$. We need the representation of $\Gamma$ to construct the
ideal strategy that realizes our correlation.

@@

Finally, we follow the proof of Proposition $4.2$ of Ref.~\cite{slofstra2017} to construct the 
representation of $\Gamma$.
\begin{definition}
\label{def:rep_gamma}
The representation $\Psi$ of $\Gamma$ on $W_2 \x W_2 \x W_{d-1}$ is defined by:
\begin{itemize}
\item for any $x$ which is also a generator of $G_1$,
\begin{align*}
	\Psi(x) = \1_{W_2} \x \Psi_1(x);
\end{align*}
\item for the generators involved in the Magic square test
\begin{align*}
	&\Psi(f_1) = X_{W_2} \x X_{W_2} \x \1_{W_{d-1}} \\
	&\Psi(g_1) = Z_{W_2} \x Z_{W_2} \x \1_{W_{d-1}} \\
	&\Psi(f_2) = X_{W_2} \x \1_{W_2} \x \1_{W_{d-1}} \\
	&\Psi(g_2) = Z_{W_2} \x \1_{W_2} \x \1_{W_{d-1}} \\
	& \Psi(m_0) = Z_{W_2} \x X_{W_2} \x \1_{W_{d-1}}\\
	& \Psi(m_1) = X_{W_2} \x Z_{W_2} \x \1_{W_{d-1}}\\
	& \Psi(m_2) = Y_{W_2} \x Y_{W_2} \x \1_{W_{d-1}}\\
	& \Psi(J) = - \1_{W_2} \x \1_{W_2} \x \1_{W_{d-1}};
\end{align*}
\item for the generators $\{ w_i \}_{i=1}^{r+5}$:
\begin{align*}
	\Psi(w_i) = Z_{W_2} \x \1_{W_{d-1}} \x \Psi_0(a_i);
\end{align*}
\item for the generators to embed the relation $f b_i f = c_i$:
\begin{align*}
	\Psi(k_{i,1}) &= X_{W_2} \x \Psi_1(b_i) = X_{W_2} \x ( \ketbra{x_1}{x_1} \x \Psi_0(a_i) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}} )\\
	\Psi(k_{i,2}) &= \ketbra{x_1}{x_2} \x \Psi_1(b_if_0) + \ketbra{x_2}{x_1} \x \Psi_1(f_0b_i)\\
	&= \ketbra{x_1x_1}{x_2x_2} \x \Psi_0(a_i) + (\ketbra{x_1x_2}{x_2x_1}+\ketbra{x_2x_1}{x_1x_2})\x\1_{W_{d-1}}\\
	&+ \ketbra{x_2x_2}{x_1x_1} \x \Psi_0(a_i)\\ 
	\Psi(k_{i,3}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_if_0b_i) + \ketbra{x_2}{x_2} \x \Psi_1(f_0) \\
	&= \ketbra{x_1}{x_1} \x X_{W_2} \x \Psi_0(a_i) +  \ketbra{x_2}{x_2} \x X_{W_2} \x \1_{W_{d-1}}\\
	\Psi(k_{i,4}) &=  \ketbra{x_1}{x_1} \x \Psi_1(b_ic_i) + \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
	&=\ketbra{x_1}{x_1} \x \1_{W_2} \x \Psi_0(a_i) +  \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
	\Psi(k_{i,5}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_i) + \ketbra{x_2}{x_2} \x \Psi_1(c_i) \\
	&=\ketbra{x_1x_1}{x_1x_1} \x \Psi_0(a_i) + (\ketbra{x_1x_2}{x_1x_2} + \ketbra{x_2x_1}{x_2x_1}) \x \1_{W_{d-1}}\\
	&+ \ketbra{x_2x_2}{x_2x_2} \x \Psi_0(a_i);
\end{align*}
\item for the generators to embed the relation $d_i b_j d_i = c_k$ with $l = (i,j,k)$:
\begin{align*}
	\Psi(k_{l,1}) &= X_{W_2} \x \Psi_1(d_i) = X_{W_2} \x X_{W_2} \x \Psi_0(a_{i}) \\
	\Psi(k_{l,2}) &= X_{W_2} \x \Psi_1(b_j) = X_{W_2} \x (\ketbra{x_1}{x_1} \x \Psi_0(a_j) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}})\\
	\Psi(k_{l,3}) &= \ketbra{x_1}{x_2} \x  \Psi_1(b_jd_i) + \ketbra{x_2}{x_1} \x \Psi_1(d_ib_j)\\
	&= \ketbra{x_1x_1}{x_2x_2} \x \Psi_0(a_{j}a_{i}) + (\ketbra{x_1x_2}{x_2x_1} + \ketbra{x_2x_1}{x_1x_2}) \x \Psi_0(a_i)\\
	&+  \ketbra{x_2x_2}{x_1x_1} \x \Psi_0(a_{i}a_{j}) \\
	\Psi(k_{l,4}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_jd_ib_j) + \ketbra{x_2}{x_2} \x  \Psi_1(d_i)\\
	&= \ketbra{x_1}{x_1} \x (\ketbra{x_2}{x_1} \x \Psi_0(a_ia_j)+ \ketbra{x_1}{x_2} \x \Psi_0(a_ja_i)) + \ketbra{x_2}{x_2} \x X_{W_2} \x \Psi_0(a_i)\\
	\Psi(k_{l,5}) &=  \ketbra{x_1}{x_1} \x \Psi_1(b_jc_k) + \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
	&=  \ketbra{x_1x_1}{x_1x_1} \x \Psi_0(a_{j}) +  \ketbra{x_1x_2}{x_1x_2} \x \Psi_0(a_{k}) +  \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
	\Psi(k_{l,6}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_j) + \ketbra{x_2}{x_2} \x \Psi_1(c_{k})\\
	&=  \ketbra{x_1x_1}{x_1x_1} \x \Psi_0(a_{j}) + (\ketbra{x_1x_2}{x_1x_2} + \ketbra{x_2x_1}{x_2x_1})\x\1_{W_{d-1}}\\
	 &+ \ketbra{x_2x_2}{x_2x_2} \x \Psi_1(a_{k}).
\end{align*}
\end{itemize}
\end{definition}
The validation of $\Psi_1$ and $\Psi$ are done in Slofstra's work \cite{slofstra2017}.

>>>>

%=======================================
\section{The linear system game $\LS(\Gamma_r)$}
\label{sec:lsg}
%=======================================
In this section, we introduce a linear system game which is a component of the full test.
This game is designed to enforce relations that should be satisfied by 
Alice and Bob's observables. The inspiration comes from 
Slofstra's seminal work~\cite{slofstra2017}, in which he
embeds the group
\begin{align}
	K = \ip{ x,y,a,b:a^2=b^2=e, ab=ba, yay^{-1} = a, yby^{-1} = ab, xyx^{-1}=y^2}
\end{align}
into a linear system game such that the relations in the definition of $K$ can be derived from the
combination of the linear equations. Then he showed the difference between exact representations
and approximate representations of $K$, which implies that the set of quantum correlation is not closed.
\hf{We generalize the relation $xyx^{-1} = y^2$ and embed the 
following relation
$
uou^{-1} = o^r 
$
for some $r \in \N$ into a linear system game.}

%------------------------------------------------------------------------
\subsection{The embedding of $uou^{-1} = o^r$}
%------------------------------------------------------------------------
The main result of this subsection is summarized in the following theorem.
\begin{theorem}
	The relation $uou^{-1} = o^r$ can be embedded in a linear system game which has
	$n(r) := 18r+85$ variables and $m(r) := 17r + 77$ equations, where each equation has $3$ variables.
\end{theorem}
We prove this by constructing the solution group $\Gamma_r$ of the linear system game,
so we denote the linear system game by $\LS(\Gamma_r)$.
\hfc{Do you prefer $\Gamma_r$ or $\Gamma(r)$? Or you have any suggestion about a symbol for this group?}
We also prove some properties of the generators of $\Gamma_r$ along the way.

We embed $uou^{-1}= o^r$ into $\Gamma_r$ in three steps, which introduce two intermediate groups $G_0$ and $G_1$ defined below.
\begin{definition}	
\label{def:g0}
	The presentation of $G_0$ has order-$2$ generators:
	\begin{align*}
		\{o_i\}_{i=1}^{r} \cup \{u_i\}_{i=1}^5
	\end{align*}
	and relations:
	\begin{align*}
	&u_3 = u_2o_1u_2 && u_4 = u_2o_2u_2 \\
	&u_5 = u_1u_3u_1 && o_2 = u_1u_4u_1\\
	&u_5 = o_1 o_r o_1,
	\end{align*}
	and when $r$ is even
	\begin{align*}
	&o_{1+2j} = o_1o_{2j}o_1 && o_{2+2j} = o_2o_{1+2j}o_2&& \text{ for } j = 1 \dots r/2 - 1;
	\end{align*}
	when $r$ is odd
	\begin{align*}
	&o_3 = o_2o_1o_2 &&
	 o_{2+2j} =o_1o_{1+2j}o_1 && o_{3+2j} = o_2o_{2j+2}o_2 &&\text{ for } j = 1 \dots (r-3)/2.
	\end{align*}
\end{definition}
\begin{proposition}
	The group $G_0$ embeds the relation 
	\begin{align}
		(u_1u_2)^j o_1o_2 (u_2u_1)^j = (o_1o_2)^{r^j}, 
	\end{align}
	for any $ j \in \N$.
\end{proposition}
The proof follows the proof of Proposition~$4.8$ of Ref.~\cite{slofstra2017}
\begin{proof}
	We prove it by induction.
	Direct calculation gives us that
	\begin{align*} 
		u_1u_2 o_1o_2 u_2u_1 = &u_1 (u_2 o_1u_2) (u_2o_2 u_2) u_1 \\
	=& (u_1 u_3 u_1) (u_1 u_4 u_1)\\
	=& u_5 o_2\\
	=& o_1o_ro_1 o_2.
	\end{align*}
	Then we substitute the definitions of $o_k$ for $k = r \dots 3$ into the equation above and
	proves the $j=1$ case.

	Now assume the statement is true for $j = n$, then for $j = n+1$
	\begin{align*}
		(u_1u_2)^{n+1} o_1o_2 (u_2u_1)^{n+1} =& u_1u_2 (o_1o_2)^{r^n} u_2u_1 \\ 
		 =& (u_1u_2 o_1o_2 u_2u_1)^{r^n} \\
		 =& (o_1o_2)^{r^{n+1}},
	\end{align*}
	where from the first line to the second line, we insert $(u_2u_1)(u_1u_2)$ between every pair of $o_1o_2$.
	Hence, the statement is true.
\end{proof}
To better characterize all the conjugation relations above and simplify the form of $G_1$ defined below, 
we relabel $u_i$ and $o_i$'s
as $a_i$'s such that
\begin{align}
	a_j := 
	\begin{cases}
	 o_j \text{ for } j = 1,2 \\
	 u_{j-2} \text{ for } j = 3\dots 7 \\
	o_{j- 5} \text{ for } j = 8 \dots r+5.
	\end{cases}
\end{align}
Then we define the set $C(r)$ of tuples $(i,j,k)$ such that
\begin{align*}
	(i,j,k) \in C(r) \iff a_ia_ja_i = a_k.
\end{align*}
The size of $C(r)$ is $r+3$. 
%We can also employ some ordering of $C(r)$ such that $C(r,j)$ is a unique tuple for 
%$j = 1 \dots r+3$.
In this way, the group $G_0$ can be presented by
$
G_0  = \ip{ \{a_i\}_{i=1}^{r+5} : C(r) }.
$
Then we define the group $G_1$.
\begin{definition}
The presentation of $G_1$ has order-$2$ generators:
\begin{align*}
	\{a_i, b_i, c_i, d_i, v_i\}_{i=1}^{r+5}, f, g, \{h_{jk}\}_{(i,j,k) \in C(r)};
\end{align*}
and relations:
\begin{align*}
	&a_i = b_ic_i = fd_i = gv_i,&& fb_if =c_i &&\text{ for } i= 1 \dots r+5 \\
	&h_{jk}b_j c_k = e,&& d_ib_jd_i = c_k &&\text{ for all } (i,j,k) \in C(r).
\end{align*}
\end{definition}
Note that the group $G_1$ is slightly different from the group $K$ used in the proof of Lemma~$4.4$ of Ref.~\cite{slofstra2017}.
We introduce the generator $g$ so that later we can associate $f$ with $g$ in linear relations of the Magic Square game.
Such relations are important for the self-testing proof.
Two important properties of $G_1$ are given in propositions below.
The first property of $G_1$ was first proved in Lemma~$4.4$ of \cite{slofstra2017}.
\begin{proposition}
	The group $G_1$ embeds relation $x_ix_jx_i = x_k$ for all $(i,j,k) \in C(r)$.
\end{proposition}
\begin{proof}
	We first show that $d_i c_j d_i = b_k$, which is because
	\begin{align*}
		d_i c_j d_i = d_i (f b_j f) d_i = f (d_i b_j d_i) f = f c_k f = b_k.
	\end{align*}
	Then, we can prove that 
	\begin{align*}
		a_i a_j a_i = f d_i b_j c_j f d_i = (f d_i b_j d_i f)(f d_i c_j d_i f) = (f c_k f)(f b_k f) = b_k c_k = a_k. 
	\end{align*}
\end{proof}
\begin{proposition}
	In the group $G_1$, the generators $f$ and $g$ commute with $a_i$ for all $i = 1 \dots r+5$.
\end{proposition}
\begin{proof}
	We can check that
	\begin{align*}
		fa_i f a_i = d_i d_i = e && g a_i g a_i = v_i v_i  = e,
	\end{align*}
	for all $i = 1 \dots r+5$.
\end{proof}
Note that there are two types of conjugacy relations in $G_1$. One is of the form
$f b_i f = c_i$ for all $i = 1 \dots r+5$. The other one is of the form 
$d_ib_jd_i = c_k$ for all $(i,j,k) \in C(r)$. For each type of the conjugacy relations, 
we are going to embed it into a different set of linear relations in $\Gamma_r$.

\begin{definition}
\label{def:gamma}
The presentation of $\Gamma_r$ has order-$2$ generators:
\begin{align*}
	J, \{a_i, b_i, c_i, d_i, v_i,w_i,\{ k_{i,j} \}_{j=1}^5\}_{i=1}^{r+5}, \{f_i,g_i,m_i\}_{i=0}^2, \{h_{jk}\}_{(i,j,k) \in C(r)}, 
	\{\{ k_{l,j} \}_{j=1}^6\}_{l \in C(r)},
\end{align*}
and relations:
\begin{itemize}
\item for all $i = 1 \dots r+5$:
\begin{align*}
	&a_i = b_ic_i = f_0d_i = g_0v_i \\
	&g_2 a_i w_i = e \\
	&f_0 f_1 f_2 = e && b_i f_2 k_{i,1} = e && k_{i,1} k_{i,2} k_{i,3} = e\\
	&f_0 k_{i,3} k_{i,4} = e && c_i k_{i,4} k_{i,5} =e && f_1 k_{i,2} k_{i,5} = e,
\end{align*}
which embed $f_0 b_i f_0 = c_i$;
\item for all $ l = (i,j,k) \in C(r)$:
\begin{align*}
	&h_{jk}b_j c_k = e\\
	&d_i k_{l,1} f_2 = e && b_j f_2 k_{l,2} = e && k_{l,2} k_{l,3} k_{l,4} = e\\
	&d_i k_{l,4} k_{l,5} = e && c_k k_{l,5} k_{l,6} =e && k_{l,1} k_{l,3} k_{l,6} = e,
\end{align*}
which embed $d_i b_j d_i = c_k$;
\item relations of a Magic Square game:
\begin{align*}
	&f_0 f_1 f_2 = e && g_0 g_1 g_2 = e &&m_0 m_1 m_2 = e \\
	&f_0 g_2 m_0 = e && f_2 g_0 m_1 = e && f_1 g_1 m_2 = J,
\end{align*}
which embed $f_0 g_0 f_0 g_0 = J$ and $f_2 g_2 f_2 g_2 = J$;
\item $J$ commutes with all the other generators.
\end{itemize}
\end{definition}
The special properties of the generators of $\Gamma_r$ are summarized in the two propositions below.
\begin{proposition}
	The group $\Gamma_r$ embeds all the conjugacy relations of $G_1$.
	It also embeds the relations: $f_0 g_0 f_0 g_0 = J$ and $f_2 g_2 f_2 g_2 = J$.
\end{proposition}
The proof of the proposition above follows the proof of Proposition $4.2$ of Ref.~\cite{slofstra2017}.
\begin{proposition}
	In the group $\Gamma_r$, the generator $f_2$ commutes with $f_0$ and $a_i$ for all $i = 1 \dots r+5$;
	the generator $g_2$ commutes with $g_0$ and $a_i$ for all $i = 1 \dots r+5$.
\end{proposition}
\begin{proof}
	We show the commutativity property of $f_2$ as an example. The proof for $g_2$ is very similar.
	The commutativity between $f_0$ and $f_2$ is immediate from the relations.
	From the relation, we can also deduce that $f_2$ commutes with $b_i$ for all $i$.
	Since $a_i =b_ic_i = b_i f_0 b_i f_0$, we know $f_2$ commutes with $a_i$.
\end{proof}

%------------------------------------------------------------------------
\subsection{A representation of $\Gamma_r$}
%------------------------------------------------------------------------
In this section we give a representation of $\Gamma_r$ which is built upon the representation 
$\Psi_0$ of $G_0$ and $\Psi_1$ of $G_1$. We need the representation of $\Gamma_r$ to construct the
ideal strategy of $\LS(\Gamma_r)$.

@@

Finally, we follow the proof of Proposition $4.2$ of Ref.~\cite{slofstra2017} to construct the 
representation of $\Gamma_r$.
\begin{definition}
\label{def:rep_gamma}
The representation $\Psi$ of $\Gamma_r$ on $W_2 \x W_2 \x W_{d-1}$ is defined by:
\begin{itemize}
\item for any $x$ which is also a generator of $G_1$,
\begin{align*}
	\Psi(x) = \1_{W_2} \x \Psi_1(x);
\end{align*}
\item for the generators involved in the Magic square test
\begin{align*}
	&\Psi(f_1) = X_{W_2} \x X_{W_2} \x \1_{W_{d-1}} \\
	&\Psi(g_1) = Z_{W_2} \x Z_{W_2} \x \1_{W_{d-1}} \\
	&\Psi(f_2) = X_{W_2} \x \1_{W_2} \x \1_{W_{d-1}} \\
	&\Psi(g_2) = Z_{W_2} \x \1_{W_2} \x \1_{W_{d-1}} \\
	& \Psi(m_0) = Z_{W_2} \x X_{W_2} \x \1_{W_{d-1}}\\
	& \Psi(m_1) = X_{W_2} \x Z_{W_2} \x \1_{W_{d-1}}\\
	& \Psi(m_2) = Y_{W_2} \x Y_{W_2} \x \1_{W_{d-1}}\\
	& \Psi(J) = - \1_{W_2} \x \1_{W_2} \x \1_{W_{d-1}};
\end{align*}
\item for the generators $\{ w_i \}_{i=1}^{r+5}$:
\begin{align*}
	\Psi(w_i) = Z_{W_2} \x \1_{W_{d-1}} \x \Psi_0(a_i);
\end{align*}
\item for the generators to embed the relation $f b_i f = c_i$:
\begin{align*}
	\Psi(k_{i,1}) &= X_{W_2} \x \Psi_1(b_i) = X_{W_2} \x ( \ketbra{x_1}{x_1} \x \Psi_0(a_i) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}} )\\
	\Psi(k_{i,2}) &= \ketbra{x_1}{x_2} \x \Psi_1(b_if_0) + \ketbra{x_2}{x_1} \x \Psi_1(f_0b_i)\\
	&= \ketbra{x_1x_1}{x_2x_2} \x \Psi_0(a_i) + (\ketbra{x_1x_2}{x_2x_1}+\ketbra{x_2x_1}{x_1x_2})\x\1_{W_{d-1}}\\
	&+ \ketbra{x_2x_2}{x_1x_1} \x \Psi_0(a_i)\\ 
	\Psi(k_{i,3}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_if_0b_i) + \ketbra{x_2}{x_2} \x \Psi_1(f_0) \\
	&= \ketbra{x_1}{x_1} \x X_{W_2} \x \Psi_0(a_i) +  \ketbra{x_2}{x_2} \x X_{W_2} \x \1_{W_{d-1}}\\
	\Psi(k_{i,4}) &=  \ketbra{x_1}{x_1} \x \Psi_1(b_ic_i) + \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
	&=\ketbra{x_1}{x_1} \x \1_{W_2} \x \Psi_0(a_i) +  \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
	\Psi(k_{i,5}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_i) + \ketbra{x_2}{x_2} \x \Psi_1(c_i) \\
	&=\ketbra{x_1x_1}{x_1x_1} \x \Psi_0(a_i) + (\ketbra{x_1x_2}{x_1x_2} + \ketbra{x_2x_1}{x_2x_1}) \x \1_{W_{d-1}}\\
	&+ \ketbra{x_2x_2}{x_2x_2} \x \Psi_0(a_i);
\end{align*}
\item for the generators to embed the relation $d_i b_j d_i = c_k$ with $l = (i,j,k)$:
\begin{align*}
	\Psi(k_{l,1}) &= X_{W_2} \x \Psi_1(d_i) = X_{W_2} \x X_{W_2} \x \Psi_0(a_{i}) \\
	\Psi(k_{l,2}) &= X_{W_2} \x \Psi_1(b_j) = X_{W_2} \x (\ketbra{x_1}{x_1} \x \Psi_0(a_j) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}})\\
	\Psi(k_{l,3}) &= \ketbra{x_1}{x_2} \x  \Psi_1(b_jd_i) + \ketbra{x_2}{x_1} \x \Psi_1(d_ib_j)\\
	&= \ketbra{x_1x_1}{x_2x_2} \x \Psi_0(a_{j}a_{i}) + (\ketbra{x_1x_2}{x_2x_1} + \ketbra{x_2x_1}{x_1x_2}) \x \Psi_0(a_i)\\
	&+  \ketbra{x_2x_2}{x_1x_1} \x \Psi_0(a_{i}a_{j}) \\
	\Psi(k_{l,4}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_jd_ib_j) + \ketbra{x_2}{x_2} \x  \Psi_1(d_i)\\
	&= \ketbra{x_1}{x_1} \x (\ketbra{x_2}{x_1} \x \Psi_0(a_ia_j)+ \ketbra{x_1}{x_2} \x \Psi_0(a_ja_i)) + \ketbra{x_2}{x_2} \x X_{W_2} \x \Psi_0(a_i)\\
	\Psi(k_{l,5}) &=  \ketbra{x_1}{x_1} \x \Psi_1(b_jc_k) + \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
	&=  \ketbra{x_1x_1}{x_1x_1} \x \Psi_0(a_{j}) +  \ketbra{x_1x_2}{x_1x_2} \x \Psi_0(a_{k}) +  \ketbra{x_2}{x_2} \x \1_{W_2} \x \1_{W_{d-1}}\\
	\Psi(k_{l,6}) &= \ketbra{x_1}{x_1} \x \Psi_1(b_j) + \ketbra{x_2}{x_2} \x \Psi_1(c_{k})\\
	&=  \ketbra{x_1x_1}{x_1x_1} \x \Psi_0(a_{j}) + (\ketbra{x_1x_2}{x_1x_2} + \ketbra{x_2x_1}{x_2x_1})\x\1_{W_{d-1}}\\
	 &+ \ketbra{x_2x_2}{x_2x_2} \x \Psi_1(a_{k}).
\end{align*}
\end{itemize}
\end{definition}
The validation of $\Psi_1$ and $\Psi$ are done in Slofstra's work \cite{slofstra2017}.
